---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MulvariateRandomForestVarImp

<!-- badges: start -->
[![R-CMD-check](https://github.com/Megatvini/VIM/workflows/R-CMD-check/badge.svg)](https://github.com/Megatvini/VIM/actions)
<!-- badges: end -->

The goal of MulvariateRandomForestVarImp package is to calculates post-hoc variable importance measures for multivariate random forests. These are given by split improvement for splits defined by feature j as measured using user-defined (i.e. training or test) examples. Importance measures can also be calculated on a per-outcome variable basis using the change in predictions for each split. Both measures can be optionally thresholded to include only splits that produce statistically significant changes as measured by an F-test. 

## Installation

You can install the released version of VIM from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("MulvariateRandomForestVarImp")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Megatvini/VIM")
```
## Example

This is a basic example which shows you how use the package:

```{r example}
library(MulvariateRandomForestVarImp)
## basic example code
set.seed(49)

X <- matrix(runif(50*5), 50, 5)
Y <- matrix(runif(50*2), 50, 2)

split_improvement_importance <- MeanSplitImprovement(X, Y)
split_improvement_importance

mean_outccome_diff_importance <- MeanOutcomeDifference(X, Y)
mean_outccome_diff_importance

```
